High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-10 notebooks/mnist.qmd
uh

@@

>>>>

```{julia}
plt, gen_delta, ces = _plot_eccco_mnist(λ = [0.1,0.1,3.0], use_energy_delta=true)
display(plt)
savefig(plt, joinpath(output_images_path, "mnist_eccco_energy_delta.png"))
```

@@

```{julia}
_regen_all_digits = true
if _regen_all_digits
    function plot_all_digits(rng=123;verbose=true,img_height=180,kwargs...)
        plts = []
        for i in 0:9
            for j in 0:9
                @info "Generating counterfactual for $(i) -> $(j)"
                plt = plot_mnist(i,j;kwargs...,rng=rng, img_height=img_height)
                !verbose || display(plt)
                plts = [plts..., plt]
            end
        end
        plt = Plots.plot(plts...; size=(img_height*10,img_height*10), layout=(10,10), dpi=300)
        return plt
    end
    plt = plot_all_digits(generator=gen_delta)
    savefig(plt, joinpath(output_images_path, "mnist_eccco_all_digits-delta.png"))
end
```
